Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-02-09 paper.tex
Add heating caption

\begin{figure*}
  \centering
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-4.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-4.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{heating_r-4.pdf}
      \caption{Internal energy, with viscous and Ohmic heating}
      \label{fig:heating-4}
    \end{subfigure}
  \mycaption{Kinetic energy as a function of time showing the development and
  measured growth rates $\gamma$ and $\lambda$ of the flute and kink
  instabilities, respectively.}{Resistivity is $\eta=10^{-4}$ and the second
  plot is a enlarged version of the first.}
\label{fig:kink_str8_ke-4}%
\end{figure*}

>>>>

\begin{figure*}
  \centering
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-4.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-4.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{heating_r-4.pdf}
      \caption{Internal energy, with viscous and Ohmic heating}
      \label{fig:heating-4}
    \end{subfigure}
  \mycaption{Kinetic energy and heating as a function of time showing the development and
  measured growth rates $\gamma$ and $\lambda$ of the flute and kink
  instabilities, respectively.}{Resistivity is $\eta=10^{-4}$ and Figure~\ref{fig:kink_ke_log-4} is a enlarged version of the first. \rev{The viscous heating associated with the flute instability (that generated before $t\approx28$) is negligible compared to that associated with the kink instability. While the isotropic model permits greater viscous heating (on the order of two orders of magnitude), the anisotropic model enhances Ohmic heating.}}
\label{fig:kink_str8_ke-4}%
\end{figure*}
